---
title: "Beach Club 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(unpivotr)
library(htmltools)
library(tidyverse)

link<-"https://www.dvcrequest.com/point-chart/beach_club_villas_2020.html"

```


```{r}
hlink<- read_html(link)

table<-hlink %>% html_nodes("table") %>% 
html_table(header=F,fill=T)

table <- table[[1]]
table
#add the table to a dataframe
dict <- as.data.frame(table)
View(dict)
```


```{r}
cells <- as_cells(table)
View(cells)
```


```{r}
(cells<-cells %>% filter(col>2,row>1) %>% select(-data_type))
cells %>% spread(row,chr) %>% 
filter(!col %in% c('4','6','10','14'))
```


```{r}
(cellstemp<-
   cells %>% spread(row,chr) %>% filter(!col %in% c('4','6','10','14'))
 )


room_view<-cellstemp[,2]
#seasons
(
adventure<-cellstemp[,3:5])
choice<-cellstemp[,6:8]
dream<-cellstemp[,9:11]
magic<-cellstemp[,12:14]
premier<-cellstemp[,15:17]

adventure<-cbind(room_view,adventure)
choice<-cbind(room_view,choice)
dream<-cbind(room_view,dream)
magic<-cbind(room_view,magic)
premier<-cbind(room_view,premier)

#use Map to row bind seasons (currently have different column names)
dfs<-data.frame(Map(c,adventure,choice,dream,magic,premier))

dfs
```

Rename columns, convert points columns (s-T,F-S) to numeric. Convert to long format with weekday as a column
```{r}

dfs<-dfs %>% rename_at(c(1,2,3,4),~c("room","season","Sun_Th","Fri_Sat")) %>%
  mutate_at(vars('Sun_Th','Fri_Sat'),as.character) %>%
  mutate_at(vars('Sun_Th','Fri_Sat'),as.numeric)

(dfl<-dfs %>% gather("weekday", "points",Sun_Th:Fri_Sat))

```

Chage room to character so that room naming can be changed
```{r}
dfl$room<-as.character(dfl$room)
#change naming of room type
dfl[dfl$room == "STUDIO(Sleeps up to 4)","room"] = "Studio"
dfl[dfl$room == "1-BEDROOM\r\n      VACATION HOME\r\n      (Sleeps up to 4)","room"] = "1-Bedroom"
dfl[dfl$room == "2-BEDROOM\r\n      VACATION HOME(Sleeps up to 8 )","room"] = "2-Bedroom"

```


We can visualize the distribution of points required by room type. First, we create a mutated dataframe with summary stats (for plotting)
```{r}

dfl_summ <- dfl %>% 
  group_by(room) %>% 
  summarize(median = median(points), sd= sd(points),mean=mean(points))


dfl %>%
  ggplot(aes(x=fct_reorder(room,points),y=points))+
  geom_boxplot()+
  geom_text(data = dfl_summ, aes(x = room, y = median, 
    label = paste("Median: ", round(median, 1))), size = 3,vjust=-0.5)+
  geom_text(data = dfl_summ, aes(x = room, y = median, 
    label = paste("SD: ", round(sd, 1))), size = 3,hjust=3,vjust=-4)+
  xlab("Room type")
```
Studios have the least variability overall


```{r}
dfl_summ2 <- dfl %>% 
  group_by(season) %>% 
  summarize(median = median(points), sd= sd(points),mean=mean(points),sevenfive=quantile(points,.75))



dfl %>%
  ggplot(aes(x=fct_reorder(season,points),y=points))+
  geom_boxplot()+
  geom_text(data = dfl_summ2, aes(x = season, y = median, 
    label = paste("Median: ", round(median, 1))), size = 3,vjust=-0.5)+
  geom_text(data = dfl_summ2, aes(x = season, y = sevenfive, 
    label = paste("SD: ", round(sd, 1))), size = 3,vjust=-1)+
  xlab("Season")
```
As these plots show, the room type determines points more than season. In other words, there is less variability in how many points will be needed for a studio vs. how many will be needed to stay during the adventure season (or any season). This is because here season is aggregated across all room types 

```{r}
dfl %>%
  group_by(room,season) %>% summarize(avg_point=mean(points)) %>%
  ungroup() %>% 
  ggplot(aes(x=fct_reorder(season,avg_point),y=avg_point, group=room))+                                       
  geom_col(aes(fill=room),position = "dodge")+
  geom_text(
    aes(label=round(avg_point,1)),
    position = position_dodge(0.9),
    vjust = 0)+
  scale_fill_manual(values = c("skyblue","grey","turquoise"))+
  xlab("Season")
```

```{r}
df20<-dfl %>% mutate(resort="Beach Club")

df20 %>% saveRDS(file = "BC2020.rds")


```

