---
title: "churn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(readxl)
retail <- read_excel("Online Retail.xlsx")
View(retail)
```


```{r}
str(retail)
retail$Country<-as.factor(retail$Country)
retail$CustomerID<-as.factor(retail$CustomerID)
```
How many unique and NA values are there for each column are in the dataset?
1. Use summarize_all to apply functions to all columns->produces wide dataframe with one column for each variable & function pair (16 total)
2. Convert to long format 

```{r}

(r<-retail %>%
  summarise_all(funs(n_distinct(.),sum(is.na(.)))) %>% gather(variable,value))

##or use list(~n_distinct(.),~...)
```


Separate the variable column on "_", create new columns for num_distinct and sum_NA
```{r,message=FALSE,warning=FALSE}
r %>% 
  separate(variable, c("variable", "stat"), sep = "_") %>%
  mutate(stat = if_else(stat == "n", "num_distinct", "sum_NA")) %>% 
  spread(stat, value)
                                                              
```

When are the NA values coming from? 
1.country
2.time

```{r}
(na_purchases<-retail %>% filter(is.na(CustomerID)) %>% select(InvoiceNo,InvoiceDate,Country))

na_purchases %>% group_by(Country) %>% ggplot(aes(x=Country))+geom_bar(stat="count")+coord_flip()

na_purchases %>% 
group_by(order_date=floor_date(InvoiceDate,"day")) %>% 
summarize(count=n()) %>% 
ggplot(aes(x=order_date,y=count))+geom_line()
```


There are 4373 unique customers in the dataset. What is the distribution of the number of purchases per customer? 
```{r,message=FALSE,warning=FALSE}
retail %>% ggplot(aes(x=CustomerID))+geom_histogram(stat="count",na.rm = T)+ylim(0,2000)
```
Some customers have a much larger number of purchases 
```{r}
retail %>% count(CustomerID,Country) %>% 
  top_n(10,n)
```


```{r}
retail<-retail %>% mutate(revenue=Quantity * UnitPrice)


rev_by_month<-retail %>% 
  select(revenue,InvoiceDate,Country) %>% 
  mutate(year_mon=floor_date(InvoiceDate,"month") %>% 
           ymd()) %>% 
  #don't have full month for Dec 2011
  filter(year_mon< ymd(20111201))


#total sales by month
monthly_sales<-rev_by_month %>% 
 group_by(year_mon) %>% 
  summarise(month_rev=sum(revenue)) %>% 
  ungroup()
  
monthly_sales %>% 
 ggplot(aes(x=year_mon,month_rev))+
    geom_line(size=.5)+
    geom_smooth(method="loess",span=.5)
  
```

##Monthly Revenue By Country

```{r}
( 
top_rev_countries<-
rev_by_month %>% group_by(year_mon,Country) %>% 
  summarise(month_rev=sum(revenue)) %>% group_by(Country) %>% summarise(total_rev=sum(month_rev)) %>% top_n(5,total_rev))

rev_by_month %>% group_by(year_mon,Country) %>% 
  
 inner_join(top_rev_countries,by="Country") %>% 
  summarise(month_rev=sum(revenue)) %>%  
  ungroup() %>% ggplot(aes(x=year_mon,month_rev,fill=Country))+
    geom_col()+ scale_fill_brewer(palette = "YlGnBu")+
  facet_wrap(~Country,scales = "free") + geom_smooth(method="lm",se=FALSE)+ scale_x_date(date_labels = "%b")+ scale_y_continuous(labels=scales::dollar)+theme_dark()
```


```{r}

```

